---
title: "Capture-Recapture and Presence-Absence Data Generation"
author: "Jack Thomas"
date: "5/9/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("data_generation_funcs.R")
```

Data generation for Blanc et al. model.

# Simulate Individuals

```{r individuals}
set.seed(512)

n <- 5
homeranges <- create_homeranges(n)
# plotting homeranges for validation
par(pty = "s")
plot(homeranges, xlim = c(0, 1), ylim = c(0, 1), main = "Home Ranges for Individuals")

text(homeranges, labels = rownames(homeranges), cex = 1.5, font = 2, pos = 3)
```

# Capture-Recapture Data

## Trap locations

Setting up the trap locations in the study area.

```{r CR-trap-locations}
set.seed(1235)

ntraps <- 3
traps <- define_traps(ntraps)
# plot traps on study area with homeranges included
par(pty = "s", mar = c(5, 4, 4, 8), xpd = TRUE)

plot(homeranges, xlim = c(0, 1), ylim = c(0, 1), main = "Home-Ranges with Camera Traps Placed")
points(traps, col = "red", pch = 15)
text(homeranges, labels = rownames(homeranges), cex = 1.5, font = 2, pos = 3)
legend("topright", inset = c(-.5, 0), c("home-range", "camera trap"), cex = .8, col = c("black", "red"), pch = c(1, 15))
```

## Trap detection probabilities

We calculate the detection probabilities of each individual for each trap.

```{r CR-trap-detection-prob}
# movement parameter
tau <- 0.55

# species capture probability
p <- 0.6

trap_detec <- calc_detection(ntraps, homeranges, traps, tau, p)

# plot individuals and their camera trap detection probabilities
# labelled for trap j. Blue label is individual i number.

for (j in 1:ntraps) {
  par(pty = "s", mar = c(5, 4, 4, 8), xpd = TRUE)
  plot(homeranges, xlim = c(0, 1), ylim = c(0, 1), main = paste0("Capture Probabilities by Trap ", j))
  points(x = traps[j, 1], y = traps[j, 2], col = "red", pch = 15)
  text(x = traps[j, 1], y = traps[j, 2], labels = paste(c("Trap", j), collapse = " "), cex = 1.5, font = 2, pos = 3)
  text(homeranges, labels = round(trap_detec[, j], 2), cex = 1, font = 2, pos = 3)
  text(homeranges, labels = rownames(homeranges), cex = 1, font = 2, pos = 2, col = "blue")
  legend("topright", inset = c(-.5, 0), c("homerange", "camera trap"), cex = .8, col = c("black", "red"), pch = c(1, 15))
}
```

## Trap interactions

Simulating the interactions of individuals with the traps over the study
period. 

```{r CR-interactions}
nsample_cap <- 5
camera_trap_full <- sim_trap_interac(homeranges, ntraps, nsample_cap, trap_detec)

# plot number of times each individual was seen by each trap
trap_counts <- rowSums(camera_trap_full, dims = 2)
for (j in 1:ntraps) {
  barplot(trap_counts[, j], names.arg = rownames(homeranges), main = paste(c("Trap", j), collapse = " "), xlab = "individual", ylab = "count")
}
```


# Presence-Absence Data

## Grid area setup

```{r presence-absence area}
nsites <- 16
regions <- setup_grid(nsites)

# plot grid cells on study area with homerange centers and individuals labeled
par(pty = "s")
plot(homeranges, xlim = c(0, 1), ylim = c(0, 1))
m <- sqrt(nsites)
for (i in 0:m) {
  abline(v = i / m)
  abline(h = i / m)
}
# individuals labeled from 1 to n
text(homeranges, labels = rownames(homeranges), cex = 1.5, font = 2, pos = 3)
```

## Simulation of presence-absence data


### Heatmap of study area

```{r plots}
library(gplots)
set.seed(1235)
nsample_pa <- 7
presence_absence <- sim_presence_absence(nsites, nsample_pa, homeranges, regions, tau)
par(pty = "s")
gen_heatmap(presence_absence, nsites)

# plot grid cells on study area with homerange centers and individuals labeled
par(pty = "s")
plot(homeranges, xlim = c(0, 1), ylim = c(0, 1), main = "Gridded Study Area")
for (i in 0:m) {
  abline(v = i / m)
  abline(h = i / m)
}
# individuals labeled from 1 to n
text(homeranges, labels = rownames(homeranges), cex = 1.5, font = 2, pos = 3)
```

# Generate Data

We can now generate our capture-recapture and presence-absence data.

```{r generate}
# number of sites
nsites <- 4**2

# number of individuals in capture history
n <- 10

# number of sampling occasions in capture-recapture
nsample_cap <- 5

# number of sampling occasions in presence-absence
nsample_pa <- 7

# amount of movement for the species
tau <- 0.25

# number of camera traps
ntraps <- 3

# homeranges for the n individuals
homeranges <- create_homeranges(n)

capture_hist <- generate_capture_hist(ntraps, nsample_cap, tau, homeranges)
capture_hist

presence_absence <- generate_presence_absence(nsites, nsample_pa, tau, homeranges)
presence_absence
```





# Output Data

Output the Capture-Recapture and Presence-Absence data into formats
that the supplementary code (Blanc 2014) can use.

```{r output}
output_data(presence_absence, capture_hist, "1")
```
