---
title: "Simulation Report"
author: "Jack Thomas"
date: '2022-08-30'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(results = "hide")
library(ggplot2)
theme_set(theme_bw())
library(readr)
require(gridExtra)
library(cowplot)
summary_stats_SimStudy4 <- read_csv("summary_stats_SimStudy4.csv")
summary_stats_SimStudy5 <- read_csv("summary_stats_SimStudy5.csv")
summary_stats_SimStudy7 <- read_csv("summary_stats_SimStudy7.csv")
summary_stats_SimStudy8 <- read_csv("summary_stats_SimStudy8ReRun.csv")
summary_stats_SimStudy10 <- read_csv("summary_stats_SimStudy10.csv")
summary_stats_SimStudy12 <- read_csv("summary_stats_SimStudy12.csv")
```

# Simulation Study Report

The simulations that will be reported are simulations 4,5, 7,8.

# First Simulation

Parameters for the first simulation (SimStudy4) were as follows:

$N \in (10,25,50)$

$\tau \in (0.25,0.35,0.45,0.55,0.65)$

nsites $=16$

nsample_cap $=5$

nsample_pa $=7$

ntraps $=3$

Each simulation (15 total) was repeated 50 times.

```{r fig.height = 2, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs. Tau - First Simulation")

ggsave("SimStudy4_credible_proportion_vs_tau.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs. Population Proportion Captured - First Simulation")

ggsave("SimStudy4_credible_proportion_vs_pop_prop.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_abline(slope = 1) +
  ggtitle("N Mean vs n Captured - First Simulation")

ggsave("SimStudy4_N_mean_vs_n_captured.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Tau - First Simulation")
ggsave("SimStudy4_N_mean_vs_tau.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = tau, y = N_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Bias vs Tau - First Simulation")
ggsave("SimStudy4_N_bias_vs_tau.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Presence-Absence Detections - First Simulation")
ggsave("SimStudy4_N_mean_vs_pa_detects.png", device = "png")

ggplot(data = summary_stats_SimStudy4, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("Standard Deviation Bias vs Tau - First Simulation")
ggsave("SimStudy4_sd_bias_vs_tau.png", device = "png")
```

# Second Simulation

Parameters for the second simulation (SimStudy5) were as follows:

$N \in (10, 25, 50,75,100,125,150,175,200)$

$\tau \in (0.15,0.20,0.25,0.30,0.35,0.4,0.45,0.5,0.55)$

nsites $=16$

nsample_cap $=5$

nsample_pa $=7$

ntraps $=3$

Each simulation (81 total) was repeated 100 times.



```{r fig.height = 10, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

SimStudy5 <- subset(summary_stats_SimStudy5, N_actual == 10 | N_actual == 50 | N_actual == 100 | N_actual == 175)

ggplot(data = SimStudy5, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Tau - Second Simulation")

ggsave("SimStudy5_credible_proportion_vs_tau.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Population Proportion Captured - Second Simulation")

ggsave("SimStudy5_credible_proportion_vs_pop_prop.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  geom_abline(slope = 1) +
  ggtitle("N Mean vs n Captured - Second Simulation")

ggsave("SimStudy5_N_mean_vs_n_captured.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Tau - Second Simulation")
ggsave("SimStudy5_N_mean_vs_tau.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = tau, y = N_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Bias vs Tau - Second Simulation")
ggsave("SimStudy5_N_bias_vs_tau.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Presence-Absence Detections - Second Simulation")
ggsave("SimStudy5_N_mean_vs_pa_detects.png", device = "png")

ggplot(data = SimStudy5, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = label_both) +
  ggtitle("Standard Deviation Bias vs Tau - Second Simulation")
ggsave("SimStudy5_sd_bias_vs_tau.png", device = "png")
```

# Third Simulation

Parameters for the third simulation (SimStudy7) were as follows:

$N \in (10, 25, 50,75,100,125,150,175,200)$

$\tau \in (0.15,0.20,0.25,0.30,0.35,0.4,0.45,0.5,0.55)$

nsites $\in (16,25,36)$

nsample_cap $=7$

nsample_pa $=5$

ntraps $\in (3,4,5)$

Each simulation (729 total) was repeated 50 times.

The simulation study failed at N_actual=200 due to a bug, so will not be included.


```{r fig.height = 10, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

SimStudy7 <- subset(summary_stats_SimStudy7, N_actual == 10 | N_actual == 175 & (nsites == 16 | nsites == 25))

ggplot(data = SimStudy7, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Tau - Third Simulation")
ggsave("SimStudy7_credible_proportion_vs_tau.png", device = "png")

ggplot(data = SimStudy7, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Population Proportion Captured - Third Simulation")
ggsave("SimStudy7_credible_proportion_vs_pop_prop.png", device = "png")

ggplot(data = SimStudy7, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps), scales = "free", labeller = label_both) +
  geom_abline(slope = 1) +
  ggtitle("N Mean vs n Captured - Third Simulation")
ggsave("SimStudy7_N_mean_vs_n_captured.png", device = "png")

ggplot(data = SimStudy7, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Tau - Third Simulation")
ggsave("SimStudy7_N_mean_vs_tau.png", device = "png")

ggplot(data = SimStudy7, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual, nsites), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs Presence-Absence Detections - Third Simulation")
ggsave("SimStudy7_N_mean_vs_pa_detects.png", device = "png")

ggplot(data = SimStudy7, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps, nsites), scales = "free", labeller = label_both) +
  ggtitle("Standard Deviation Bias vs Tau - Third Simulation")
ggsave("SimStudy7_sd_bias_vs_tau.png", device = "png")
```

# Fourth Simulation

Parameters for the fourth simulation (SimStudy8) were as follows:

$N \in (10, 25, 50,75,100,125,150,175,200,500)$

$\tau \in (0.15,0.20,0.25,0.30,0.35,0.4,0.45,0.5,0.55)$

nsites $\in (8**2,9**2,10**2)$

nsample_cap $=7$

nsample_pa $=5$

ntraps $\in (3,4,5,6)$

Each simulation (1296 total) was repeated 50 times.


```{r fig.height = 10, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

pop_labeller <- function(x) paste0("Actual Population: ", x)

SimStudy8 <- subset(summary_stats_SimStudy8, ( N_actual == 200) & nsites == 100 & ntraps == 6)

ggplot(data = SimStudy8, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  geom_hline(yintercept = 0.95, lty = 2, color = "red") +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Credible Proportion")
ggsave("SimStudy8_credible_proportion_vs_tau.png", device = "png", dpi = 300)

ggplot(data = SimStudy8, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  geom_hline(yintercept = 0.95, lty = 2) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Population Proportion Captured") +
  ylab("Credible Proportion")
ggsave("SimStudy8_credible_proportion_vs_pop_prop.png", device = "png", dpi = 300)


N_mean_n_captured_8 <- ggplot(data = SimStudy8, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  geom_abline(slope = 1) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  ggtitle("A)") +
  xlab("Number Captured") +
  ylab("Population Estimate")
ggsave("SimStudy8_N_mean_vs_n_captured.png", device = "png", dpi = 300)

cor(SimStudy8$n_captured, SimStudy8$N_mean)



N_mean_tau_8 <- ggplot(data = SimStudy8, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  geom_hline(data = SimStudy8, aes(yintercept = N_actual), lty = 2, color = "red") +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Population Estimate")
N_mean_tau_8
ggsave("SimStudy8_N_mean_vs_tau.png", device = "png", dpi = 300)

cred_width_tau_8 <- ggplot(data = SimStudy8, mapping = aes(x = tau, y = credible_width)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Credible Interval Width")
cred_width_tau_8
ggsave("SimStudy8_cred_width_vs_tau.png", device = "png", dpi = 300)


ggsave("SimStudy8_N_mean_cred_width_tau.png", arrangeGrob(N_mean_tau_8, cred_width_tau_8))


SimStudy8_pa <- subset(summary_stats_SimStudy8, (N_actual == 200) & (nsites == 100) & ntraps == 6)
N_mean_pa_detects_8 <- ggplot(data = SimStudy8_pa, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  xlab("Presence-Absence Detections") +
  ylab("Population Estimate") +
  theme(plot.margin = margin(10, 20, 10, 10))
ggsave("SimStudy8_N_mean_vs_pa_detects.png", device = "png", dpi = 300)

pa_detects_n_captured_8 <- ggplot(data = SimStudy8_pa, mapping = aes(x = pa_detects, y = n_captured)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Presence-Absence Detections") +
  ylab("Number Captured")
ggsave("SimStudy8_pa_detections_vs_n_captured.png", device = "png", dpi = 300)

ggsave("SimStudy8_N_mean_pa_detects_n_captured.png", arrangeGrob(N_mean_pa_detects_8, pa_detects_n_captured_8))

sd_bias_tau_8 <- ggplot(data = SimStudy8, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ggtitle("A)") +
  ylab("Standard Deviation Bias")
ggsave("SimStudy8_sd_bias_vs_tau.png", device = "png", dpi = 300)



sd_bias_pop_prop_8 <- ggplot(data = SimStudy8, mapping = aes(x = n_captured / N_actual, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Population Proportion Captured") +
  ylab("Standard Deviation Bias")
ggsave("SimStudy8_sd_bias_pop_prop.png", device = "png", dpi = 300)



ggplot(data = SimStudy8, mapping = aes(x = tau, y = psi0_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual), scales = "free", labeller = as_labeller(pop_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Psi Mean")
ggsave("SimStudy8_psi0_mean_tau.png", device = "png", dpi = 300)

SimStudy8_N_actual <- subset(summary_stats_SimStudy8, (nsites == 100) & ntraps == 3)

var_color <- "tau"

ggplot(data = SimStudy8_N_actual, mapping = aes(x = N_actual, y = N_mean, color = get(var_color))) +
  geom_point() +
  geom_abline(slope = 1, color = "red") +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Actual Population") +
  ylab("Population Estimate") +
  guides(color = guide_legend(title = var_color))
ggsave("SimStudy8_N_mean_vs_N_actual.png", device = "png", dpi = 300)
```

# Fifth Simulation

Simulation 10 varied:

  $N \in (10,100,200)$
  
  $\tau \in (0.15,0.30,0.55)$
  
  nsites $\in (49,64,81)$
  
  nsample_cap $\in (8,10,12,14)$
  
  nsample_pa $\in (8,10,12,14)$
  
  ntraps $\in (3,4,5,6)$


```{r fig.height = 10, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

SimStudy10 <- subset(summary_stats_SimStudy10, N_actual == 200 & nsample_cap >= 8 & nsample_cap <= 10 & nsample_pa >= 8 & nsample_pa <= 10 & ntraps == 6)

ggplot(data = SimStudy10, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps, nsample_cap), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Tau")
ggsave("SimStudy10_credible_proportion_vs_tau.png", device = "png", height = 100, limitsize = F, dpi = 300)

ggplot(data = SimStudy10, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps, nsample_cap), scales = "free", labeller = label_both) +
  geom_hline(yintercept = 0.95, lty = 2) +
  ggtitle("Credible Proportion vs Population Proportion Captured")
ggsave("SimStudy10_credible_proportion_vs_pop_prop.png", device = "png", dpi = 300)


ggplot(data = SimStudy10, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps, nsample_cap), scales = "free", labeller = label_both) +
  geom_abline(slope = 1) +
  ggtitle("N Mean vs. n Captured")
ggsave("SimStudy10_N_mean_vs_n_captured.png", device = "png", dpi = 300)

ggplot(data = SimStudy10, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(N_actual, ntraps, nsample_cap), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs. Tau")
ggsave("SimStudy10_N_mean_vs_tau.png", device = "png", dpi = 300)

ggplot(data = SimStudy10, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(tau, nsites, nsample_pa), scales = "free", labeller = label_both) +
  ggtitle("N Mean vs. Presence-Absence Detections")
ggsave("SimStudy10_N_mean_vs_pa_detects.png", device = "png", dpi = 300)

ggplot(data = SimStudy10, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(ntraps, nsample_pa, nsample_cap), scales = "free", labeller = label_both) +
  ggtitle("Standard Deviation Bias vs. Tau")
ggsave("SimStudy10_sd_bias_vs_tau.png", device = "png", dpi = 300)
```


# 6th Simulation


```{r fig.height = 10, fig.width = 10, results='hide', message=FALSE, warning=FALSE, echo=FALSE}

p_labeller <- function(x) paste0("Capture Probability: ", x)

SimStudy12 <- subset(summary_stats_SimStudy12, N_actual == 500 & nsites == 64 & ntraps == 5 & delta == 1 & sigma == 1)

cred_prop_tau_12 <- ggplot(data = SimStudy12, mapping = aes(x = tau, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  geom_hline(yintercept = 0.95, lty = 2) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Credible Proportion")
ggsave("SimStudy12_credible_proportion_vs_tau.png", device = "png", dpi = 300)

ggplot(data = SimStudy12, mapping = aes(x = n_captured / N_actual, y = credible_proportion)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  geom_hline(yintercept = 0.95, lty = 2) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Population Proportion Captured") +
  ylab("Credible Proportion")
ggsave("SimStudy12_credible_proportion_vs_pop_prop.png", device = "png", dpi = 300)


ggplot(data = SimStudy12, mapping = aes(x = tau, y = credible_width)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Credible Interval Width")
ggsave("SimStudy12_cred_width_vs_tau.png", device = "png", dpi = 300)



N_mean_n_captured_12 <- ggplot(data = SimStudy12, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  geom_abline(slope = 1) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  ggtitle("B)") +
  xlab("Number Captured") +
  ylab("Population Estimate")
ggsave("SimStudy12_N_mean_vs_n_captured.png", device = "png", dpi = 300)

ggsave("N_mean_n_captured_8_12.png", arrangeGrob(N_mean_n_captured_8, N_mean_n_captured_12), height = 10)


cor(SimStudy12$n_captured, SimStudy12$N_mean)

ggplot(data = SimStudy12, mapping = aes(x = tau, y = N_mean)) +
  geom_point() +
  geom_hline(yintercept = 500, linetype = "dashed", color = "red") +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Population Estimate")
ggsave("SimStudy12_N_mean_vs_tau.png", device = "png", dpi = 300)


SimStudy12_pa <- subset(summary_stats_SimStudy12, (N_actual == 10) & (nsites == 64) & ntraps == 5 & delta == 1 & sigma == 1)
ggplot(data = SimStudy12_pa, mapping = aes(x = pa_detects, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  xlab("Total Presence-Absence Detections") +
  ylab("Population Estimate") +
  theme(plot.margin = margin(10, 20, 10, 10))
ggsave("SimStudy12_N_mean_vs_pa_detects.png", device = "png", dpi = 300)

ggplot(data = SimStudy12_pa, mapping = aes(x = n_captured, y = pa_detects)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Number Captured") +
  ylab("Presence-Absence Detections")
ggsave("SimStudy12_pa_detections_vs_n_captured.png", device = "png", dpi = 300)


sd_bias_tau_12 <- ggplot(data = SimStudy12, mapping = aes(x = tau, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ggtitle("B)") +
  ylab("Standard Deviation Bias")
ggsave("SimStudy12_sd_bias_vs_tau.png", device = "png", dpi = 300)


ggsave("sd_bias_tau_8_12.png", device = "png", dpi = 300, arrangeGrob(sd_bias_tau_8, sd_bias_tau_12))

sd_bias_pop_prop_12 <- ggplot(data = SimStudy12, mapping = aes(x = n_captured / N_actual, y = sd_bias)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Population Proportion Captured") +
  ylab("Standard Deviation Bias")
ggsave("SimStudy12_sd_bias_pop_prop.png", device = "png", dpi = 300)

ggsave("sd_bias_pop_prop_8_12.png", device = "png", dpi = 300, arrangeGrob(sd_bias_pop_prop_8, sd_bias_pop_prop_12))

ggplot(data = SimStudy12, mapping = aes(x = tau, y = psi0_mean)) +
  geom_point() +
  facet_wrap(vars(p), scales = "free", labeller = as_labeller(p_labeller)) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Tau") +
  ylab("Psi Mean")
ggsave("SimStudy12_psi0_mean_tau.png", device = "png", dpi = 300)


SimStudy12_delta_sigma <- subset(summary_stats_SimStudy12, N_actual == 500 & nsites == 64 & ntraps == 5 & p == 0.75)

cor(SimStudy12_delta_sigma$n_captured, SimStudy12_delta_sigma$N_mean)

N_mean_n_captured_delta_sigma_12 <- ggplot(data = SimStudy12_delta_sigma, mapping = aes(x = n_captured, y = N_mean)) +
  geom_point() +
  facet_wrap(vars(delta, sigma), scales = "free", labeller = label_both) +
  geom_abline(slope = 1) +
  theme(plot.margin = margin(10, 10, 10, 10)) +
  xlab("Number Captured") +
  ylab("Population Estimate")
ggsave("SimStudy12_N_mean_vs_n_captured_delta_sigma.png", device = "png", dpi = 300)
```
